Effects of sexual selection on non-sexual fitness components: a meta-analysis

### 2018-05-20 meta_analysis_sexual_selection_pop_fitness.Rmd
plot with both bayesian and frenq

#And plot the results
pd <- position_dodgev(height = 0.65)
EnvSex.metaanalysis <- predictions.complete2 %>% 
      mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%
  ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
  geom_errorbarh(aes(xmin = predictions.complete2$ci.lb, 
                     xmax = predictions.complete2$ci.ub,
                     color = Sex), height = 0, position = pd, show.legend = F) +
  geom_point(aes(size=nn), position = pd, shape=21, color = "grey20") + 
  scale_size(guide = 'none')+
  ylab("Environment\n")+
  xlab("\nEffect Size (Hedges' g)")+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")+
  guides(fill = guide_legend(reverse=T, override.aes = list(size = 3)))+
  scale_x_continuous(limits = c(-0.2, 1), breaks = c(-0.2, 0, 0.2, 0.4, 0.6, 0.8, 1))+

@@

We can run a bayesian model using the brms package. The model has the same moderators as the REML approach used above. 
```{r, warning=FALSE}
library(rstan) #Note that installation requires some effort
library(brms) 
library(backports) #seems to be a dependency
```

@@

#Add columns for Environment and Sex
posterior_fit$Sex <- c("Male", "Both", "Female", "Male", "Both", "Female")
posterior_fit$Environment <- c("Benign_Male", "Benign_Both", "Benign_Female", "Stressful_Male", "Stressful_Both", "Stressful_Female")

@@

```{r, fig.height=8, fig.width=8}
posterior_fit %>% ggplot(aes(x=value, y = Environment, fill = Sex))+
  geom_density_ridges2(alpha = 0.75)+
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
    ylab("Environment\n")+
  xlab("\nPosterior Effect Size (Hedges' g)")+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")+
  guides(fill = guide_legend(reverse=T, override.aes = list(size = 0.5)))+
  scale_x_continuous(limits = c(-0.5, 1.2), breaks = c(-1, -.5, 0, 0.5, 1))+

@@

  theme(panel.spacing = unit(0.5, "lines"),
        text = element_text(size=14),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.text = element_text(size=14), 
        legend.title=element_text(size=14, 
                                  face = "bold"),
        axis.title.x = element_text(hjust = 0.5, size = 14),
        axis.title.y = element_text(size = 14),
        axis.text.y = element_text(angle = 0),
        plot.title = element_text(size = 14))

```
<br></br>
**Figure X** Posterior fitted values for Hedges' g using the same model as above

>>>>

#And plot the results
pd <- position_dodgev(height = 0.65)
predictions.complete2 <- predictions.complete2 %>% 
      mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%
  mutate(Environment = replace(as.character(Environment), Environment == "Stressed", "Stressful"),
         Environment = replace(Environment, Environment == "Unstressed", "Benign"))
 EnvSex.metaanalysis <- predictions.complete2 %>% ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
  geom_errorbarh(aes(xmin = predictions.complete2$ci.lb, 
                     xmax = predictions.complete2$ci.ub,
                     color = Sex), height = 0, position = pd, show.legend = F) +
  geom_point(aes(size=nn), position = pd, shape=21, color = "grey20") + 
  scale_size(guide = 'none')+
  ylab("Environment\n")+
  xlab("\nEffect Size (Hedges' g)")+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")+
  guides(fill = guide_legend(reverse=T, override.aes = list(size = 3)))+
  scale_x_continuous(limits = c(-0.2, 1), breaks = c(-0.2, 0, 0.2, 0.4, 0.6, 0.8, 1))+

@@

We can run a bayesian model using the brms package. The model has the same moderators as the REML approach used above. 
```{r, warning=FALSE, message = FALSE}
library(rstan) #Note that installation requires some effort
library(brms) 
library(backports) #seems to be a dependency
devtools::install_github("mvuorre/brmstools")
library(brmstools) 
```

@@

#Add columns for Environment and Sex
posterior_fit$Sex <- c("Male", "Both", "Female", "Male", "Both", "Female")
posterior_fit$Environment <- c("Benign", "Benign", "Benign", "Stressful", "Stressful", "Stressful")

@@

```{r, fig.height=5, fig.width=5}

pd <- position_dodgev(height = 0.3)
posterior.plot <- posterior_fit %>% ggplot()+
  geom_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.4, scale = 0.6, position = position_nudge(y = 0.15), height = 10)+
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
    ylab("Environment\n")+
  xlab("\nPosterior Effect Size (Hedges' g)")+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")+
  guides(fill = guide_legend(reverse=T, override.aes = list(size = 0.5)))+
  scale_x_continuous(limits = c(-0.5, 1.2), breaks = c(-1, -.5, 0, 0.5, 1))+

@@

  theme(panel.spacing = unit(0.1, "lines"),
        text = element_text(size=14),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.text = element_text(size=14), 
        legend.title=element_text(size=14, 
                                  face = "bold"),
        axis.title.x = element_text(hjust = 0.5, size = 14),
        axis.title.y = element_text(size = 14),
        axis.text.y = element_text(angle = 0),
        plot.title = element_text(size = 14))

both.plots <- posterior.plot + 
  geom_point(data = predictions.complete2, 
             aes(x = pred, y = Environment, size=nn, fill = Sex), 
             shape=21, color = "grey20", position = pd, show.legend = F) +

  geom_errorbarh(data = predictions.complete2, 
                 aes(x= pred, xmin = predictions.complete2$ci.lb,
                     xmax = predictions.complete2$ci.ub, y = Environment,
                     color = Sex), 
                 height = 0, show.legend = F, position = pd)+
    scale_y_discrete(expand=c(0.075,0))

both.plots

svg("figures/both_plot.svg", width=6, height=6)
both.plots
dev.off()
```
<br></br>
**Figure X** Posterior fitted values for Hedges' g using the same model as above
